Refinements for open automata

### 2022-02-10 2021-Refinement/paper/refinementarticle.tex
samll changes ...

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove the following:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$, we will then have:\\ $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ and
${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j} = \beta_{23xj}}$\\
On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
In addition $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

>>>>

We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove the following:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,\,\,{\displaystyle \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in vars(s_3)}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in J'_1$:\\
Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
We have also:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
As $t_{13}$ and $t_{23}$ are built with the same transitions of $A_3$  (up renaming) so we can deduce:
\begin{align*}
{\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} & \Rightarrow  {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3} \beta_{13j} = \beta_{23xj}}\\
& \Rightarrow {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
In addition as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$
